\vspace{1.0cm} \LARGE \bf Revealing the competitive dynamics of influenza viruses through evolutionary cartography \\ or \\ Charting antigenic drift and evolutionary success of seasonal influenza lineages

### 2013-01-29 flux.tex
Minor revisions.

%%% TITLE %%%
\title{\vspace{1.0cm} \Large \bf 
Charting antigenic drift and evolutionary success of seasonal influenza lineages \\
or \\
Integrating influenza antigenic dynamics with molecular evolution \\
or \\
Integrating antigenic cartography and molecular evolution to characterize predictors of evolutionary success of seasonal influenza lineages \\
or \\
Predicting the evolutionary success of seasonal influenza lineages through the integration of antigenic cartography and molecular evolution \\
or \\
Cartographic characterization of antigenic and evolutionary dynamics of seasonal influenza viruses
}

>>>>

%%% TITLE %%%
\title{\vspace{1.0cm} \Large \bf 
Charting antigenic drift and evolutionary success of seasonal influenza lineages \\
or \\
Integrating influenza antigenic dynamics with molecular evolution \\
or \\
Predicting the evolutionary success of seasonal influenza lineages through the integration of antigenic cartography and molecular evolution \\
or \\
Cartographic characterization of the antigenic, evolutionary and competitive dynamics of seasonal influenza viruses \\
or \\
Integrating antigenic dynamics with molecular evolution to characterize competition within and between seasonal influenza lineages \\
}
